Type Refinements for the Working Class

### 2015-11-20 paper.tex
Correct computational approximation definition (bad notation still)

\newcommand\HypJ[2]{#1\ \ (#2)}
\newcommand\GenJ[2]{\vert_{\IMode{#1}}\; #2}
\newcommand\HPGenJ[4]{\vert^{\IMode{#1}\parallel\IMode{#2}}_{\IMode{#3}}\; #4}

@@

In any topos $\mathcal{E}$, for an object $X$ we can define the object of
relations on $X$ as the exponential $\Define{\Pow{X}}{\Omega^X}$. Then, the
data of such a relation is contained in a natural transformation
$\Of{R}{\Hom{\mathcal{E}}{\mathbb{1}}{\Pow{X}}}$.

@@

As a convenience, we'll also define this judgment over vectors of bound terms and valences:
\[
  \infer{
    \SBinRel{R_{\vec{v}}}{\Upsilon}{\vec{E}}{\vec{F}}
  }{
    \forall\Member{(E,F,v)}{(\vec{E},\vec{F},\vec{v})}.\
    \SBinRel{R_v}{\Upsilon}{E}{F}
  }
\]

Now, we can extend $R_\tau$ to a new relation $[R_\tau]$ on closed expressions
which respects a single ``layer'' of computation, defined pointwise in the following way:
\begin{gather*}
  \infer{
    \SBinRel{[R_\tau]}{\Upsilon}{M}{N}
  }{
    \Eval{\Upsilon}{\tau}{M}{\App{\vartheta}{\Vec{E}}} &
    \Eval{\Upsilon}{\tau}{N}{\App{\vartheta}{\Vec{F}}} &
    \Lookup{\CanOperators}{\vartheta}{\MkArity{\vec{v}}{\tau}} &
    \SBinRel{R_{\vec{v}}}{\Upsilon}{\vec{E}}{\vec{F}}
  }
\end{gather*}

Because $[-_\tau]$ is monotonic, it has a greatest fixed point, which we will
call \emph{applicative approximation},
$\Of{\preceq_\tau}{\Hom{\Sets^\SCtx}{\mathbb{1}}{\Pow{\Exprs_\tau^2}}}$,
written pointwise as $\SBinRel{\preceq_\tau}{\Upsilon}{M}{N}$.

>>>>

\newcommand\HypJ[2]{#1\ \ \left(#2\right)}
\newcommand\GenJ[2]{\vert_{\IMode{#1}}\; #2}
\newcommand\HPGenJ[4]{\vert^{\IMode{#1}\parallel\IMode{#2}}_{\IMode{#3}}\; #4}

@@

\begin{remark}
  In any topos $\mathcal{E}$, for an object $X$ we can define the object of
  relations on $X$ as the exponential $\Define{\Pow{X}}{\Omega^X}$. Then, the
  data of such a relation is contained in a natural transformation
  $\Of{R}{\Hom{\mathcal{E}}{\mathbb{1}}{\Pow{X}}}$.
\end{remark}

@@

As a matter of convenience, we'll also define this judgment over vectors of bound terms and valences:
\[
  \infer{
    \SBinRel{R_{\vec{v}}}{\Upsilon}{\vec{E}}{\vec{F}}
  }{
    \forall\Member{(E,F,v)}{(\vec{E},\vec{F},\vec{v})}.\
    \SBinRel{R_v}{\Upsilon}{E}{F}
  }
\]

Now, we can extend $R_\tau$ to a new relation $[R_\tau]$ on closed expressions
which respects a single ``layer'' of computation, defined pointwise in the following way:
\begin{gather*}
  \infer{
    \SBinRel{[R_\tau]}{\Upsilon}{M}{N}
  }{
    \left(\Eval{\Upsilon}{\tau}{N}{\App{\vartheta}{\Vec{F}}}
    \quad
    \SBinRel{R_{\vec{v}}}{\Upsilon}{\vec{E}}{\vec{F}}\right)
    \quad
    \text{supposing}
    \quad
    \left(
      \Eval{\Upsilon}{\tau}{M}{\App{\vartheta}{\Vec{E}}},
      \Lookup{\CanOperators}{\vartheta}{\MkArity{\vec{v}}{\tau}}
    \right)
  }
\end{gather*}

\begin{definition}[Computational Approximation]
Because $[-_\tau]$ is monotonic, it has a greatest fixed point, which we will
call \emph{computational approximation},
$\Of{\preccurlyeq_\tau}{\Hom{\Sets^\SCtx}{\mathbb{1}}{\Pow{\Exprs_\tau^2}}}$,
written pointwise as $\SBinRel{\preccurlyeq_\tau}{\Upsilon}{M}{N}$.
\end{definition}

\begin{definition}[Computational Equivalence]
  Two terms are said to be \emph{computationally equivalent} when they approximate each other:
  \[
    \infer{
      \SBinRel{\sim_\tau}{\Upsilon}{M}{N}
    }{
      \SBinRel{\preccurlyeq_\tau}{\Upsilon}{M}{N} &
      \SBinRel{\preccurlyeq_\tau}{\Upsilon}{N}{M}
    }
  \]
\end{definition}
